Cleaning Data

### 2021-07-28 cleaning_aid.Rmd
cleaning_aid.Rmd

@@

# omics type
omics <- x$Omics.type
omics_split <- strsplit(omics,", ")
omics <- unlist(omics_split)
table(omics)

@@

# App used
App <-x$App.used
App_split <- strsplit(App,", ")
App <- unlist(App_split)
table(App)

# Gene set version
GSV <-x$GS.version
table(GSV)

>>>>

```{r,begin}

knitr::opts_chunk$set(fig.width=7, fig.height=7)

@@

```{r,columns1}

par(mar=c(5,12,3,1))

# omics type
omics <- x$Omics.type
omics_split <- strsplit(omics,", ")
omics <- unlist(omics_split)
res <- table(omics)
res <- res[order(res)]
res
barplot(tail(res,20),horiz=TRUE,las=1,cex.names = 0.7, xlab="no. analyses",
        main = "Omics type", xlim=c(0,600))
grid()

```{r,columns2}

@@

# App used
App <-x$App.used
App_split <- strsplit(App,", ")
App <- unlist(App_split)
table(App)
```

```{r,columnsX}
par(mar=c(5,7,3,1))
# Gene set version
GSV <-x$GS.version
res <- table(GSV)
res
barplot(tail(res,20),horiz=TRUE,las=1,cex.names = 1, xlab="no. analyses",
        main = "Gene set version defined", xlim=c(0,1600))
grid()
